Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2020-12-04 manuscript.tex
Clarify 'how many acini per lung' we chose [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/b888dd09a43ba4c9cab06a58ba4001ff2b0c5b04.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/b888dd09a43ba4c9cab06a58ba4001ff2b0c5b04/checks
https://github.com/habi/acinar-analysis-manuscript/runs/401082577

\emph{A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/786681} and has been submitted to the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}}.
\emph{This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/commit/c56a516d2a7b3c0eec6f0b820c5d8744313bc31b...e0a6b5fb8ba2cead74aa2be2fa4e0cec35c58591}{has been updated} since the original submission}.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/e0a6b5fb8ba2cead74aa2be2fa4e0cec35c58591/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/e0a6b5fb8ba2cead74aa2be2fa4e0cec35c58591}{habi/acinar-analysis-manuscript@e0a6b5f}
on December 4, 2020.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/786681} and has been submitted to the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.
This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...b888dd09a43ba4c9cab06a58ba4001ff2b0c5b04}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/b888dd09a43ba4c9cab06a58ba4001ff2b0c5b04/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/b888dd09a43ba4c9cab06a58ba4001ff2b0c5b04}{habi/acinar-analysis-manuscript@b888dd0}
on December 4, 2020.
